EEG Waveform Analysis with applications to Brain Computer Interfaces

### 2018-08-16 sensors.tex
Update with a little modification about someting I remember

In contrast, automatic processing, or quantitative EEG (qEEG), was based first on analog electronic devices and later on computerized digital processing methods \citep{Jansen1991}.  They implemented mathematically and algorithmically complex procedures to decode the information associated with a clinical condition, or even some higher cognitive state \citep{Yuste2017}.  The best materialization of the automatic processing of EEG signals rests in the BCI discipline, where around $71.2\%$ is based on noninvasive EEG \citep{Guger2017}.

@@

\begin{table}[H]
\caption{Subjective EEG characterization methods found in the surveyed literature.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Method}	& \textbf{Phenomena} & \textbf{Reference}	\\
\midrule
Characteristic Shape           & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Rising and Falling Phase      & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Pronounced plateau      & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Ripples and Wiggles     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Sinusoidal Shape        & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Sawtooth                     & Motor Imagery, Sleep &  \citep{Cacioppo2007, Mak2010} \\
Sharpness or Spike-like     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Rectangular     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Wicket Shape     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Peak and Trough Sharpness Ratio     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Symmetry between rise and decay phase     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Slope Ratio    & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Positive vs Negative Ratio    & Sleep K-Complex &  \citep{Cacioppo2007, Mak2010} \\
Base-to-Peak Amplitude     & ERP  &  \citep{Cacioppo2007, Mak2010} \\
Peak-to-Peak Amplitude     & ERP  &  \citep{Cacioppo2007, Mak2010} \\
Latency                                 & ERP  & \citep{Cacioppo2007, Mak2010}  \\
Integrated Activity               & ERP, Epilepsy & \citep{Cacioppo2007, Shah2015} \\
Cross-Correlation                & ERP, Epilepsy, Sleep & \citep{Cacioppo2007, Shah2015} \\
Coupling \\ Cross Frequency,  Phase-Amplitude, Phase-Phase     & Sleep & $20\%$ \\
Period Amplitude Analysis  & ERP, Epilepsy & \citep{Cacioppo2007, Shah2015} \\
\bottomrule
\end{tabular}
\label{tab:results}
\end{table}

>>>>

In contrast, automatic processing, or quantitative EEG (qEEG), was based first on analog electronic devices~\citep{Jestico1977} and later on computerized digital processing methods \citep{Jansen1991}.  They implemented mathematically and algorithmically complex procedures to decode the information associated with a clinical condition, or even some higher cognitive state \citep{Yuste2017}.  The best materialization of the automatic processing of EEG signals rests in the BCI discipline, where around $71.2\%$ is based on noninvasive EEG \citep{Guger2017}.

@@

\begin{table}[H]
\caption{Subjective EEG characterization methods found in the surveyed literature.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Method}	& \textbf{Phenomena} & \textbf{Reference}	\\
\midrule
Rounded                                & $\alpha$-Waves & \citep{Schomer2010} \\
Characteristic Shape           & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Rising and Falling Phase      & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Pronounced plateau      & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Ripples and Wiggles     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Sinusoidal Shape        & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Sawtooth                     & Motor Imagery, Sleep &  \citep{Cacioppo2007, Mak2010} \\
Sharpness or Spike-like     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Rectangular     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Wicket Shape     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Peak and Trough Sharpness Ratio     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Symmetry between rise and decay phase     & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Slope Ratio    & Epilepsy &  \citep{Cacioppo2007, Mak2010} \\
Positive vs Negative Ratio    & Sleep K-Complex &  \citep{Cacioppo2007, Mak2010} \\
Base-to-Peak Amplitude     & ERP  &  \citep{Cacioppo2007, Mak2010} \\
Peak-to-Peak Amplitude     & ERP  &  \citep{Cacioppo2007, Mak2010} \\
Latency                                 & ERP  & \citep{Cacioppo2007, Mak2010}  \\
Integrated Activity               & ERP, Epilepsy & \citep{Cacioppo2007, Shah2015} \\
Cross-Correlation                & ERP, Epilepsy, Sleep & \citep{Cacioppo2007, Shah2015} \\
Coupling \\ Cross Frequency,  Phase-Amplitude, Phase-Phase     & Sleep & $20\%$ \\
Period Amplitude Analysis  & ERP, Epilepsy & \citep{Cacioppo2007, Shah2015} \\
\bottomrule
\end{tabular}
\label{tab:results}
\end{table}
